### 2022-02-01 manuscript/manuscript.Rmd
Update manuscript.Rmd

plot_list <- map(topic_order, plotDomains) # create list of plots for the 20 statistical topics
```

>>>>

plot_list <- map(topic_order, plotDomains) # create list of plots for the 20 statistical topics

# to save individual plots for twitter
# for(i in 1:20){
#    ggsave(plot = plot_list[[i]], file = here('manuscript','figs','twitter',paste("topic",i,".png",sep="")), width = 6, height = 8, units = "in", dpi = 300)
#  }
```
